% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\graphicspath{ {./images/} }

% Please include a clear, concise, and descriptive title
\title{CPD Report} 

% Please do not change the subtitle
\subtitle{COMP230 CPD Report}

% Please put your student number in the author field
\author{1507516}

\begin{document}

\maketitle

%Relevance and Importance (to games industry)

%How the skills affects my work

%Propose a solution to this problem in referenace to SMART

%Specific – target a specific area for improvement.
%Measurable – quantify or at least suggest an indicator of progress.
%Assignable – specify who will do it.
%Realistic – state what results can realistically be achieved, given available resources.
%Time-related – specify when the result(s) can be achieved.

\section{Introduction}
This report will cover five main issues I faced in the first semester of year two and will propose some SMART solutions that may help resolve these issues.
The top five issues I consider my main problems are: Communication in a Large Team, Equal Distribution of Workload, Confidence in Requesting Support, Community engagement and Transitioning from Low level Languages such as C++ to Higher Level languages such as C\#.

\section{Communication in a Large Team}

%Importance
Working and communicating well in a large team is critical when working in a business. Furthermore this skill is very relevant to the games industry because as a programmer I will have to communicate well across different disciplines, such as Design, Art etc..


%How it affects my work
This issues affected the quality of my Comp230 collaborative project as I had to work with a large team of 12 people. I had to communicate with the programmers and designers on that team to understand what functionality they wanted for the networking component. However the communication that I had wasn't all that regular, especially towards the end of the semester because I had so much other work to be doing along side this project.


%Solution
\subsection{How I aim to overcome this problem}
Over the course of next semester when I will continue development of the lobby system, I will aim to fix this by dedicating one or possibly two days a week to be in their studio and work along side the programmers to get more of an understanding about what to do for the component.




\section{Equal Distribution of Workload}
%Importance
When having a lot of projects to work on simultaneously, it is sometimes hard to distribute the work out evenly so each project gets the same amount of time, and one project doesn't get put off till the last minute. 

%How it affects my work
This affected my work a lot this year because there were some projects that I favored a lot over some of the others, thus I spent more of my time to a project that was going well, instead of spending time on the projects that weren't going so well.

%Solution
\subsection{How I aim to overcome this problem}
To try and overcome this issue I will propose a working routine for next semester, where I can only work on one of the projects in a specified day. For example, work on one project from Mon-Tues and another from Wed-Thu. This will allow for even distribution of projects and force me to work on projects that I may not enjoy as much, but that need to get done.
%Google calener


\section{Confidence in Requesting Support}
%Afective domain (mental state)
%assertive training
%Importance
Having the confidence to ask for help is important throughout life in general, however having confidence in the games industry will mean you can get further and be more successful.


%How this affects my work
In the first Semester I was stuck on trying to optimize my Comp220 project for a long time, and in the end just gave up. This could of been solved if I asked my lecturer or one of my peers to help my try and understand how to go about improving it.
This affected the quality of my work by making me spend most of my time focusing on a part of the project that wasn't marked, when I could of spent that time implementing new components to the game.


%Solution
\subsection{How I aim to overcome this problem}
Starting next semester I will aim to create pull requests whenever I get stuck, so hopefully my teachers and peers will be able to help me out with anything I'm really stuck on.



\section{Community engagement}
%proceural
%Importance
Engaging with the community, whether that community is the audience for you game, or your programmer colleagues is important because you can get feedback from them and feed that forward into your future improvements.


%How this affects my work
I felt I have not contributed much to community engagement this semester.
Next semester I will plan on having more of a presence on github, and make comments on my peers code.
I only made one pull request in the first semester, which was for a scheduled peer review session.

%Solution
\subsection{How I aim to overcome this problem}
Next Semester when I am working on my projects and get really stuck on something, I will create a pull request.Furthermore I will try and answer any pull requests created by coursemates.



%Cognativie deomain
%Moving from C++ to C#
%From low end to highend witha framework already mplemented
\section{Transitioning from Low level Languages such as C++ to Higher Level languages such as C\#}
%Importance
There are a lot of different programming languages being used in the games industry, and each language has a different level of framework behind it, so being able to understand a switch between low level languages to high level languages is important.

%How this affects my work
In the first semester I have been mainly using C++ and C\# which both have different levels of framework behind them. I have better understand of C++ as I studied it last year and over the summer, however when transitioning to C\# in Unity, there are a lot of high level constructs that I had a hard time understanding. For example getting a component of an object.

%Solution
\section{How I aim to overcome this}
Over the Christmas break and beginning of next semester I will be playing around with unity to try and understand how certain features work, such as getting a component of an object and modifying it.

\section{Conclusion}
Despite having these issues, I have enjoyed all the projects this semester, and hopefully when I put these proposed solutions into action over the coming months, my professional practice and development will become a lot better.


\end{document}
